Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
more temp

The effect of seasonality of resources on sociality can be directly measured by
differences in sociality in discrete time windows. Using an ordinal multilayer
network consisting of 20 discrete time windows throughout the study period, we
observed periods of increased sociality in caribou on Fogo Island (Figure
\@ref(fig:temp)). Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A).
<!-- not done -->

Furthermore, the selection of time windows is essential for both capturing life
stages of interest and having sufficient data to construct robust networks.
Social phenotypes can change over ontogeny in ways that can affect fitness
[@Berger_2015; @Brent_2017]. Further complicating the issue, individuals can
vary in their rate of development [@Tarka_2018]. This variation can make
defining the appropriate temporal scale for testing the fitness implications of
an individual’s social phenotype over different stages of ontogeny difficult.
However, considering fine temporal scales has been show to provide insight across developmental
stages that may otherwise be missed [@Turner_2017]. Furthermore, given the non-independent nature of social interactions and associations,
especially over time, it can be challenging to test hypotheses about social dynamics with a
suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
multilayer networks, ordinal layers of discrete time windows provide a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods. <!--hmm-->

>>>>

The effect of seasonality of resources on sociality can be directly measured by
differences across discrete time windows. Using an ordinal multilayer network
consisting of 20 discrete time windows throughout the study period, we observed
periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
overlap correspond to seasons of low resource availability [Peigner_2019].
Similarly, individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) B).

The selection of time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017]. Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.

Finally, it is crucial to consider sufficient data to construct robust networks
when selecting time windows and study periods.
